\documentclass[margin]{res}  
\usepackage{helvet}
\usepackage{hyperref}
\textheight=700pt
\begin{document}
\newcommand{\company}{}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{Joseph Cuffney}
\address{\href{https://cuffney.com}{cuffney.com}\\\href{http://github.com/jwc2790}{github.com/jwc2790}}
\address{josephcuffney@gmail.com\\585-503-2714}
%-------------------------------------------------------------------------------

\begin{resume}
%-------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------

\section{EXPERIENCE}

\employer{\href{http://nike.com}{Nike Valiant Labs.}}
\location{Portland, OR}
\dates{Jun. 2018 - Present}
\title{\textbf{Sr. Software Engineer}}

\begin{position}\\
\textit{\href{https://wearecultivator.com}{Cultivator.}}:\\
- Worked on a team to design and implement a robust scalable set of tools to create a curated NikeID shopping experience in a two sided creator driven marketplace.\\
- Worked closely with the team to set up and constantly improve a scalable and flexible system architecture which included serverless architecture models, react on aws elastic beanstalk, and lambda driven services.\\
- Worked with Nike's existing notification team to implement e-commerce and factory related emails to consumers via a java application and Salesforce.

\end{position}

\employer{\href{http://nike.com}{Nike Innovation Accelerator.}}
\location{Portland, OR}
\dates{Aug. 2017 - Jun. 2018}
\title{\textbf{Sr. Lead Full Stack Engineer}}

\begin{position}\\
\textit{\href{https://traintandem.com}{Tandem Personal Training.}}:\\
- Designed and implemented a subscription based service serving clients and personal trainers in the Portland metro area.\\
- Set up a scalable and flexible system architecture which included setting up Craft CMS on Elastic Beanstalk.\\
- Set up various AWS Lambda functions to handle payments and Stripe web hooks. 
- Implemented a two party payment system which included subscription invoicing, transfers, refunds, and automated subscription management.\\
- Worked closely with marketing and design team to iterate on content and A/B tests to increase conversion rates.\\
- Worked on a team to do project management tasks such as sprint planning, backlog grooming, and estimation.\\
- Worked closely with marketing and customer support teams to support acquisition efforts.

\end{position}


\employer{\href{http://theprogrampdx.com}{The Program PDX.}}
\location{Portland, OR}
\dates{Oct. 2015 - Aug. 2017}
\title{\textbf{Technical Lead}}

\begin{position}\\
- Took technical ownership of projects to deliver digital experiences utilizing a wide range of stacks including React/Redux, Express, Spring Boot,  Middleman, and Craft.\\
- Oversaw the scoping, estimation, sprint planning, and implementation of projects while simultaneously contributing to the primary development of others.\\
- Worked with clients as well as project managers to improve processes and foster team growth and an environment of open communication and learning.\\
- Mentored other coworkers though problems with debugging and learning modern web technologies including but not limited to React/Redux.\\
- Worked developer operations tasks such as server configuration, environment setup,  and continuous integration using of tools like Jenkins, Ansible, Docker, and Digital Ocean.

\textit{Nike: The Locker.}: \\
- Worked on a team of 3 developers to create a React/Redux application that keeps track of Nike athlete's contact information, products, and preferences.
\par

\textit{Red Bull: Express API.}: \\
- Implemented a ExpressJS Node API for a Red Bull web experience with 100\% test coverage, data validation, and documentation generation.
\par

\textit{\href{http://earnyour.name/}{Earn Your Name.}}: \\
- Implemented a Naive Bayes classifier for classifying users based on a set of training data into a set number of categories given their riding data pulled from Strava.\\
- created the front end web application using React/Redux.
\par

\textit{Nike: Air Max Day CDP.}: \\
- Implemented Spring Boot Java API to persist the applications voting with Redis.\\
- Created a static web experience to celebrate Nike Air Max's anniversary which was viewed over 10 million times. 
\par

\textit{\href{https://www.ledlenserusa.com/ledbylight.html}{Led Lenser: Led by Light.}}: \\
- Implemented static microsite with a strong focus on CSS3 transitions and aesthetics.\\
- Used Ruby's Middleman, Contentful, and web hooks to generate static page content.
\par

\textit{\href{https://www.http://www.teamwass.com/}{Wasserman.}}: \\
- Worked on a team to implement CMS solution for Wasserman built on Docker, Craft CMS, and AWS.
- Was responsible for writing 2 [PHP] craft cms plugins for both Twitter and Instagram integration into their news page.
\par
\end{position}

\employer{Contract}
\location{Portland, OR}
\dates{June 2016 - June 2016}
\title{\textbf{Webpack Consulting}}
\begin{position}
- Helped explain and implement a local startups VueJS webpack configuration and integrated it into their development and production build processes. \\
- Illustrated use of plugins such as BrowserSync, ExtractTextPlugin, and optimize for their builds\\ 
- Taught startup's developer the concept of webpack chunks and how they can help improve application performance. As a result this reduced their main bundle size by 50\% and cut page load times in half across the application.
\end{position}

\employer{\href{http://discoverklamath.com}{Discover Klamath.}}
\location{Portland, OR}
\dates{Dec. 2016 - Present}
\title{\textbf{Freelance Developer}}
\begin{position}
- Maintained and developed the Klamath county tourism website built on craft cms.
- Improved SEO score to have the site show up on the first page of Google for desired keywords.
- Configured infrastructure on AWS including automated deployment with TravisCI.
\end{position}

\employer{\href{http://moog.com}{Moog Inc.}}
\location{Buffalo, NY}
\dates{Jan. 2014 - Aug. 2014}
\title{\textbf{Web Developer Coop}}
\begin{position}
- Developed a fault tree analysis web application which improved report quality, speed, and consistency and is now used across all US locations.\\
- Wrote a document parser to convert various file types to plain text which is then run though an report engine to save engineers up to a day of time per report.
\end{position}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{\href{https://rit.edu}{Rochester Institute of Technology.}}, Rochester, NY\\
{\sl Bachelor of Science}, Computer Science\\
{\sl GPA}: 3.56


%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{COMPUTER\\SKILLS}

\textbf{Languages}: Java, Python, JavaScript, SQL/TSQL, Go, C++, C, .NET (C\#).\\
\textbf{Dev Ops}: AWS, Cloud Formation, Docker, Jenkins, Digital Ocean, Ansible.\\
\textbf{Web Frameworks}: React, Express, Struts 2, Spring, Django, Middleman, Craft CMS.\\
\textbf{Testing Frameworks}: Mocha, Chai, J Unit, Selenium.\\
\textbf{Tools}: Git, vi[m], Webpack, Tmux.\\
\textbf{Development Processes}: Agile development, Test-driven development.\\
% \textbf{Certifications}: AWS Certified Solutions Architect.\\
\textbf{E-commerce Platforms}: Stripe, Shopify.\\
\textbf{Marketing Tools}: Intercom, Google Analytics, Google Optimize.


%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	PROJECTS SECTION
%-------------------------------------------------------------------------------
% \section{OTHER PROJECTS}
% \par

% \textbf{Traveling Salesman Problem.}: \\
% - Implemented [4] solutions to the traveling salesman problem and performed a analysis of their time
% and space complexities.
% \par

% \textbf{Neural Network Language Detection}:\\
% - 3-layer feed forward neural network. Distinguishes English, Dutch, and Italian with 98\% accuracy
% \par

% \textbf{A* With Optimal Path Simplification}: \\
% - Implemented A* search algorithm to find an optimal path approximation though an image of a
% building’s floor map.
% \par

% \textbf{AI For Cable Car}: \\
% - Finished 4th in a competition of 60 teams to create an AI for the game Cable Car. \\

% More projects available upon request.
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	References
%-------------------------------------------------------------------------------
\section{References}
- Sean Kennedy - (503) 780-4542\\
- Reid Bloomquist - (503) 481-4844\\
- Dylan Smith - (503) 222-1442\\
 \\
More references available upon request.
%-------------------------------------------------------------------------------
\end{resume}
\end{document}